Paper_Results

### 2025-02-15 Paper_Results.Rmd
update figures

ggsave("Figures/Example2.jpg",
  plot = p1,
  width = 10.2,
  height = 4.5)

@@

ggsave(  "Figures/Example4.jpg",
  plot = combined_plot,
  width = 10.2,
  height = 5.5)

@@

ggsave( "Figures/Example3.jpg",
  plot = combined_plot,
  width = 11.5,
  height = 6.5)
```

@@

ggsave( "Figures/Example_var.jpg",
  plot = p2,
  width = 8,
  height = 7)

@@

ggsave(  "Figures/figure7.jpg",
  plot = p7,
  width = 10,
  height = 5)

>>>>

ggsave("Figures/Figure4_Example2.jpg",
  plot = p1,
  width = 10.2,
  height = 4.5)

@@

ggsave(  "Figures/Figure5_Example4.jpg",
  plot = combined_plot,
  width = 10.2,
  height = 5.5)

@@

ggsave( "Figures/Figure6_Example3.jpg",
  plot = combined_plot,
  width = 11.5,
  height = 6.5)
```

@@

ggsave( "Figures/Figure7_Example_var.jpg",
  plot = p2,
  width = 8,
  height = 7)

@@

ggsave(  "Figures/Figure8.jpg",
  plot = p7,
  width = 10,
  height = 5)
